### 2020-02-03 ncov.tex
tweaks

\section*{Abstract}
A novel coronavirus (2019-nCoV) has recently emerged as a global threat. 
As the epidemic progresses, many disease modelers have prioritized
\bmb{focused on? (this is what we say in the body of the paper)} estimating the basic reproductive number \Ro, the average number of secondary cases caused by a primary case.
These efforts are valuable;
however, their modeling approaches and the resulting estimates vary widely, despite relying on similar data sources. \bmb{why is this a problem/opportunity? ``however'' suggests some sort of problem, but it isn't explicitly stated what it is \ldots}
% don't need {\ } after \Ro because we use xspace
Here, we present a framework for comparing and combining different estimates of \Ro across a wide of models by decomposing it into three key quantities (the exponential growth rate $r$, the mean generation interval $\bar G$, and the generation-interval dispersion $\kappa$) and apply our framework to early estimates of \Ro for the 2019-nCoV outbreak.
Our results emphasize the importance of propagating uncertainties in all three quantities, in particular in the shape of the generation-interval distribution.

@@

We evaluate six disparate models published online between January 24--26, 2020 that estimated \Ro for the 2019-nCoV outbreak \citep{imaincov, liuncov, majumderncov, readncov, riouncov, zhaoncov}. 
We use our framework to construct pooled estimates for the three key quantities: $r$, $\bar G$, and $\kappa$;
the pooled estimates reflect the uncertainties present in modeling approaches and their underlying assumptions.
We use these pooled estimates to illustrate the importance of propagating different sources of error, particularly uncertainty in both the growth rate and the generation interval. 
We also use our framework to unravel \bmb{tease apart?} which assumptions of these different models led to their different estimates and confidence intervals.

@@

\begin{figure}[!ht]
\includegraphics[width=\textwidth]{figure2.pdf}
\caption{
  \textbf{Effects of $r$, $\bar G$, and $\kappa$ on the estimates of \Ro.}
  \bmb{May I suggest that you use {\tt theme\_set(theme\_bw(base\_size=18))} (or some large value) rather than (or in addition to) increasing the sizes of the points and lines?}
We compare estimates of \Ro under five scenarios that propagate different combinations of uncertainties.
\textbf{base}: \Ro estimates based on the median estimates of $\mu_r$, $\mu_G$, and $\mu_\kappa$.
\textbf{growth rate}: \Ro estimates based on the the posterior distribution of $\mu_r$ while using median estimates of $\mu_G$ and $\mu_\kappa$.
\textbf{GI mean}: \Ro estimates based on the the posterior distribution of $\mu_G$ while using median estimates of $\mu_r$ and $\mu_\kappa$.
\textbf{growth rate + GI mean}: \Ro estimates based on the the joint posterior distributions of $\mu_r$ and $\mu_G$ while using a median estimate of $\mu_\kappa$.
\textbf{all}: \Ro estimates based on the joint posterior distributions of  $\mu_r$, $\mu_G$, and $\mu_\kappa$.
Vertical lines represent the 95\% confidence intervals.
}
\label{fig:eff}
\end{figure}

>>>>

\section*{Abstract}
A novel coronavirus (2019-nCoV) has recently emerged as a global threat. 
As the epidemic progresses, many disease modelers have focused on estimating the basic reproductive number \Ro, the average number of secondary cases caused by a primary case.
These efforts are valuable;
however, their modeling approaches and the resulting estimates vary widely, despite relying on similar data sources. \bmb{why is this a problem/opportunity? ``however'' suggests some sort of problem, but it isn't explicitly stated what it is \ldots}
% don't need {\ } after \Ro because we use xspace
Here, we present a framework for comparing and combining different estimates of \Ro across a wide of models by decomposing it into three key quantities (the exponential growth rate $r$, the mean generation interval $\bar G$, and the generation-interval dispersion $\kappa$) and apply our framework to early estimates of \Ro for the 2019-nCoV outbreak.
Our results emphasize the importance of propagating uncertainties in all three quantities, in particular in the shape of the generation-interval distribution.

@@

We evaluate six disparate models published online between January 24--26, 2020 that estimated \Ro for the 2019-nCoV outbreak \citep{imaincov, liuncov, majumderncov, readncov, riouncov, zhaoncov}. 
We use our framework to construct pooled estimates for the three key quantities: $r$, $\bar G$, and $\kappa$;
the pooled estimates reflect the uncertainties present in modeling approaches and their underlying assumptions.
We use these pooled estimates to illustrate the importance of propagating different sources of error, particularly uncertainty in both the growth rate and the generation interval. 
We also use our framework to tease apart which assumptions of these different models led to their different estimates and confidence intervals.

@@

\begin{figure}[!ht]
\includegraphics[width=\textwidth]{figure2.pdf}
\caption{
  \textbf{Effects of $r$, $\bar G$, and $\kappa$ on the estimates of \Ro.}
We compare estimates of \Ro under five scenarios that propagate different combinations of uncertainties.
\textbf{base}: \Ro estimates based on the median estimates of $\mu_r$, $\mu_G$, and $\mu_\kappa$.
\textbf{growth rate}: \Ro estimates based on the the posterior distribution of $\mu_r$ while using median estimates of $\mu_G$ and $\mu_\kappa$.
\textbf{GI mean}: \Ro estimates based on the the posterior distribution of $\mu_G$ while using median estimates of $\mu_r$ and $\mu_\kappa$.
\textbf{growth rate + GI mean}: \Ro estimates based on the the joint posterior distributions of $\mu_r$ and $\mu_G$ while using a median estimate of $\mu_\kappa$.
\textbf{all}: \Ro estimates based on the joint posterior distributions of  $\mu_r$, $\mu_G$, and $\mu_\kappa$.
Vertical lines represent the 95\% confidence intervals.
}
\label{fig:eff}
\end{figure}
